%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref} % Enable hyperlinks.
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Zorian Thornton} % Your name
\address{Ph.D Student, Genome Sciences, Seattle,WA} % Address or description
\address{(+1) 804-316-1769 \\ zoriant15@gmail.com} % Your phone number and email
\address{\href{https://zorian15.github.io}{zorian15.github.io}}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Washington - Seattle,WA} \hfill {\em Sep. 2019 - Present}
\\ Ph.D in Genome Sciences \hfill { GPA: 3.8 / 4.0} \smallskip \\
{\bf Virginia Tech - Blacksburg,VA} \hfill {\em Aug. 2015 - May 2019}
\\ B.Sc Statistics \hfill { GPA: 3.7 / 4.0} \smallskip
\\{\bf Virginia Tech - Blacksburg,VA} \hfill {\em Aug. 2015 - May 2019}
\\ B.Sc Computational Modeling and Data Analytics \hfill { GPA: 3.6 / 4.0 } \smallskip  \\
Minors in Mathematics and Computer Science
\end{rSection}




%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

%% Matsen Group candidate
{\bf Fred Hutchison Cancer Research Center} \hfill { \em Seattle,WA}\\
{Doctoral Candidate, advised by Frederick Matsen IV} \hfill {\em July 2021 - Present}
\begin{itemize}
    \item Developing \texttt{torchdms}: a flexible modeling framework for fitting neural networks using PyTorch to deep mutational scanning experiments.
    The goal of \texttt{torchdms} is to infer a \emph{fitness landscape} of viral and antibodies that accurately predicts quantitative phenotypes of unseen protein variants while preserving biophysically interpretable parameters.
\end{itemize}

{\bf Virginia Tech Statistical Applications and Innovations Group} \hfill {\em Blacksburg, VA} \\
{Associate Collaborator} \hfill {\em June 2019 - Sept. 2019}
\begin{itemize}
    \item Statistics consultant to Virginia Tech graduate students and faculty.
\end{itemize}

{\bf Nielsen} \hfill {\em Chicago, IL} \\
{Data Science Intern} \hfill {\em June 2018 - Aug. 2018}
\begin{itemize}
    \item Implemented statistical framework to identify possible OCR errors in scanned receipt data and implemented pipeline to correct errors
    \end{itemize}

{\bf Virginia Tech Math Emporium} \hfill {\em Blacksburg, VA} \\
{Instructional Assistant} \hfill {\em Jan. 2017 - Aug. 2018}
\begin{itemize}
    \item Teaching assistant for introductory math courses including differential and integral calculus, graph theory, differential equations, and linear algebra
\end{itemize}
\end{rSection}



%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Programming Languages, Tools, and Concepts}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Preferred Programming Languages \ & Python, R, C/C++ \\
Numerical Tools \ & PyTorch, numpy, pandas \\
Dev Tools \& Environments  & Git, Jupyter \\
Other Programming Languages \ &  Java, MATLAB, PHP, SAS, SQL
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Publications}

\begin{itemize}

    \item El Moustaid, F., \textbf{Thornton, Z.}, Slamani, H., Ryan, S. and Johnson, LR (2021). Predicting temperature-dependent transmission suitability of bluetongue virus in livestock. \emph{Parasites Vectors}, 14(1), pp.1-14..

    \item Keller, A., Chavez, J.D., Eng, J.K., \textbf{Thornton, Z.} and Bruce, J.E. (2018). Tools for 3D Interactome Visualization. \emph{Journal of proteome research}, 18(2), pp.753-758.
\end{itemize}

\end{rSection}



\end{document}
